More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
desciption de l'ABP

@@

>>>>

\begin{figure}[t]
  \centerline{
   \includegraphics[width=8cm]{XFIG/ABP-Schema}
   }
   \caption{Schema of the ABP example}  \label{ABP:Schema}
\end{figure}

@@

\section{Running Example}
To illustrate this work, we use the well-known Alternate bit protocol
(ABP), that provides safe transport of data between two processes,
over unsafe media. This protocol has been described and studied using
many approaches, because it is small enough, and can be easily
verified using exact finite models. Our version here is more
ambitious, encoding both the data and the control bits in a symbolic
way. One can imagine that this could easily be extended using bounded
integers, as in the Sliding window protocol, or with more complex data
structures, in order to verify realistic protocols.

Fig. \ref{ABP:Schema} shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying unsafe network is modelled by two media,
carrying the message together with a control bit on one way, and an
acknowledge back form $Q$ to $P$. The media can be perfect (safe), or
faulty (losing or duplicating messages) as shown in
Fig. \ref{schema:ABP-media}.

The full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.
